Supporting Information

### 2018-04-17 SupportingInformation.Rmd
plot fixing,adding chunk for BMR data

## Phylogenetic data  \label{Phylo_data}
```{r calculation_phylo_data, echo=F, results="hide"}
source("getcopula.R")
phylo_dat<-read.csv("./Data/Anolis/contrasts.csv",header = T)
# Input :
#        data : a dataframe : phylo_dat with dim.=[99 x 14]
#        i, j : column indices of data frame to get bivariate data set, should be (i,j)<=13
#        ploton : logical for option plots of raw data and it's copula representation
# Output : 
#        a cop rank matrix for the raw data
phylo_dat_fn<-function(data,i,j,ploton=T){

  data<-data[,2:dim(phylo_dat)[2]]
  d<-data[,c(i,j)]

  v_phylo<-getcopula(d=d,rankon = T,ploton = F)

  if(ploton==T){
    op<-par(mfrow=c(1,2))
    plot(d[,1],d[,2],col="blue")
    getcopula(d=d,rankon = T,ploton = T)
    par(op)
  }
  return(v_phylo)
}

@@

### Non-parametric analysis of tail dependence \label{Ex_SoilCN_NPA}
<!--Do the intensive part of the analysis, calculating stats on the data and surrogates-->
```{r stat_soilCN_graphic_approach, echo=F, cache=T, cache.extra=list(seed,v_CN,mtime("CopulaFunctions_flexible.R"),mtime("copsurrog2d.R"))}
source("CopulaFunctions_flexible.R")
source("copsurrog2d.R")
set.seed(seed)

#utility function for calculating all the stats we want
calcstats<-function(v,f,nm)
{
  #calculate the stats
  res<-c()
  for (lbd in seq(from=0,to=0.9,by=0.1))
  {
    res<-c(res,f(v[,1],v[,2],lbd,lbd+.1))
  }

  #name the result vector
  h<-paste(nm,c(seq(from=0,to=0.9,by=0.1)),"to",
                    c(seq(from=0,to=0.9,by=0.1)+.1),sep='')
  h<-gsub(".","p",h,fixed=T)
  names(res)<-h

  return(res)
}

#Do the kendall surrogates
cop<-normalCopula(.5,2)
numsurrog<-1000
surv_K<-copsurrog2d(v_CN,cop,"kendall",numsurrog)

#Do the spearman surrogates
surv_S<-copsurrog2d(v_CN,cop,"spearman",numsurrog)

#utility function for calculating fractions of surrogates 
#with a stat smaller than that of data, i.e., fraction of 
#surrogates for which the stat value on the data is bigger
fracwork<-function(dvals,surrvals)
{
  frac<-NA*numeric(length(dvals))
  names(frac)<-names(dvals)
  for (counter in 1:length(frac))
  {
    frac[counter]<-sum(surrvals[counter,]<dvals[counter])
  }
  return(frac)
}

#now work with the correlation stats
corstats_d<-calcstats(v_CN,Corbds,"Cor")
corstats_K<-apply(FUN=calcstats,X=surv_K,MARGIN=3,f=Corbds,nm="Cor")
corstats_frac_K<-fracwork(corstats_d,corstats_K)

corlmcoru_d<-unname(corstats_d[1]-corstats_d[length(corstats_d)])
corlmcoru_K<-corstats_K[1,]-corstats_K[length(corstats_d),]
corlmcoru_frac_K<-sum(corlmcoru_K<corlmcoru_d)
corstats_K<-apply(FUN=quantile,X=corstats_K,MARGIN=1,prob=c(.005,0.25,.975,.995))

corstats_S<-apply(FUN=calcstats,X=surv_S,MARGIN=3,f=Corbds,nm="Cor")
corstats_frac_S<-fracwork(corstats_d,corstats_S)

corlmcoru_S<-corstats_S[1,]-corstats_S[length(corlmcoru_d),]
corlmcoru_frac_S<-sum(corlmcoru_S<corlmcoru_d)
corstats_S<-apply(FUN=quantile,X=corstats_S,MARGIN=1,prob=c(.005,0.25,.975,.995))

#now work with the P stats
Pbds_wrap<-function(vi,vj,lb,ub)
{
  return(Pbds(vi,vj,lb,ub)$abs_res)
}

Pstats_d<-calcstats(v_CN,Pbds_wrap,"P")
Pstats_K<-apply(FUN=calcstats,X=surv_K,MARGIN=3,f=Pbds_wrap,nm="P")
Pstats_frac_K<-fracwork(Pstats_d,Pstats_K)

PlmPu_d<-unname(Pstats_d[1]-Pstats_d[length(Pstats_d)])
PlmPu_K<-Pstats_K[1,]-Pstats_K[length(Pstats_d),]
PlmPu_frac_K<-sum(PlmPu_K<PlmPu_d)
Pstats_K<-apply(FUN=quantile,X=Pstats_K,MARGIN=1,prob=c(.005,0.25,.975,.995))

Pstats_S<-apply(FUN=calcstats,X=surv_S,MARGIN=3,f=Pbds_wrap,nm="P")
Pstats_frac_S<-fracwork(Pstats_d,Pstats_S)

PlmPu_S<-Pstats_S[1,]-Pstats_S[length(Pstats_d),]
PlmPu_frac_S<-sum(PlmPu_S<PlmPu_d)
Pstats_S<-apply(FUN=quantile,X=Pstats_S,MARGIN=1,prob=c(.005,0.25,.975,.995))

#now work with the D2 stats
D2stats_d<-calcstats(v_CN,D2bds,"Dtwo")
D2stats_K<-apply(FUN=calcstats,X=surv_K,MARGIN=3,f=D2bds,nm="Dtwo")
D2stats_frac_K<-fracwork(D2stats_d,D2stats_K)

D2umD2l_d<-D2stats_d[length(D2stats_d)]-D2stats_d[1]
D2umD2l_K<-D2stats_K[length(D2stats_d),]-D2stats_K[1,]
D2umD2l_frac_K<-sum(D2umD2l_K<D2umD2l_d)
D2stats_K<-apply(FUN=quantile,X=D2stats_K,MARGIN=1,prob=c(.005,0.25,.975,.995))

D2stats_S<-apply(FUN=calcstats,X=surv_S,MARGIN=3,f=D2bds,nm="Dtwo")
D2stats_frac_S<-fracwork(D2stats_d,D2stats_S)

D2umD2l_S<-D2stats_S[length(D2stats_d),]-D2stats_S[1,]
D2umD2l_frac_S<-sum(D2umD2l_S<D2umD2l_d)
D2stats_S<-apply(FUN=quantile,X=D2stats_S,MARGIN=1,prob=c(.005,0.25,.975,.995))
```

<!--Now create the plot and save it to the results folder-->
```{r plot_soilCN_graphic_approach, results='hide', echo=F}
x<-seq(from=0.05,to=0.95,by=0.1)
xlimits<-c(0,1)

#plotting layout, units inches
xht<-0.5
ywd<-0.5
titleht<-.25
panht<-1.5
panwd<-3
gap<-.05
totwd<-ywd+2*panwd+2*gap
totht<-xht+3*panht+3*gap+titleht
pdf(file="./Results/stat_results/stat_soilCN/CNdata_NonparamTailDep.pdf",width=totwd,height=totht)

#plot kendall results on the left panels, spearman on right,
#cor in top panels, then P, then D2 on bottom panels

#kendall, cor
par(fig=c(ywd/totwd,
          (ywd+panwd)/totwd,
          (xht+2*panht+2*gap)/totht,
          (xht+3*panht+2*gap)/totht),
    mai=c(0,0,0,0),mgp=c(3,.15,0),tcl=-.25)
ylimits_cor<-range(corstats_d,corstats_K,corstats_K)
ylimits_cor[2]<-ylimits_cor[2]+.3*diff(ylimits_cor)
plot(x,corstats_d,type='l',col="red",xlim=xlimits,ylim=ylimits_cor,
     xaxt='n')
mtext(side=3,line=0,text="Kendall-preserving surrogates")
mtext(side=2,line=1,text="Partial correlation")
axis(side=1,labels=F)
lines(x,corstats_K[1,],type='l',lty='dotted')
lines(x,corstats_K[2,],type='l',lty='dashed')
lines(x,corstats_K[3,],type='l',lty='dashed')
lines(x,corstats_K[4,],type='l',lty='dotted')
text(xlimits[1],ylimits_cor[1],labels='A',cex=1.5,adj=c(.5,0))
fracplot<-function(fracs,ylims)
{
  for (counter in 1:length(fracs))
  {
    ptxt<-''
    if (fracs[counter]>.975*numsurrog)
    {
      ptxt<-paste(">",fracs[counter],sep='')
    } 
    if (fracs[counter]<.025*numsurrog)
    {
      ptxt<-paste("<",numsurrog-fracs[counter],sep='')
    }
    yht<-ylims[2]-.1*diff(ylims)
    text(x[counter],yht,ptxt,adj=c(0.5,.5),cex=0.5,srt=90)
  }
}
fracplot(corstats_frac_K,ylimits_cor)
vlineplot<-function(x,ylims)
{
  for (counter in 1:length(x))
  {
    lines(rep(x[counter]-(x[2]-x[1])/2,2),ylims,type='l',lty='dotted')
  }
  lines(rep(x[length(x)]+(x[2]-x[1])/2,2),ylims,type='l',lty='dotted')
}
vlineplot(x,ylimits_cor)

#spearman, cor
par(fig=c((ywd+panwd+gap)/totwd,
          (ywd+2*panwd+gap)/totwd,
          (xht+2*panht+2*gap)/totht,
          (xht+3*panht+2*gap)/totht),
    mai=c(0,0,0,0),mgp=c(3,.15,0),tcl=-.25,new=T)
plot(x,corstats_d,type='l',col="red",xlim=xlimits,ylim=ylimits_cor,
     xaxt='n',yaxt='n')
mtext(side=3,line=0,text="Spearman-preserving surrogates")
axis(side=1,labels=F)
axis(side=2,labels=F)
lines(x,corstats_S[1,],type='l',lty='dotted')
lines(x,corstats_S[2,],type='l',lty='dashed')
lines(x,corstats_S[3,],type='l',lty='dashed')
lines(x,corstats_S[4,],type='l',lty='dotted')
text(xlimits[1],ylimits_cor[1],labels='B',cex=1.5,adj=c(.5,0))
fracplot(corstats_frac_S,ylimits_cor)
vlineplot(x,ylimits_cor)

#kendall, P
par(fig=c(ywd/totwd,
          (ywd+panwd)/totwd,
          (xht+panht+gap)/totht,
          (xht+2*panht+gap)/totht),
    mai=c(0,0,0,0),mgp=c(3,.15,0),tcl=-.25,new=T)
ylimits_D2<-range(D2stats_d,D2stats_K,D2stats_K)
ylimits_D2[2]<-ylimits_D2[2]+.3*diff(ylimits_D2)
ylimits_P<-range(Pstats_d,Pstats_K,Pstats_K)
ylimits_P[2]<-ylimits_P[2]+.3*diff(ylimits_P)
plot(x,Pstats_d,type='l',col="red",xlim=xlimits,ylim=ylimits_P,xaxt='n')
axis(side=1,labels=F)
mtext(side=2,line=1,text="P")
lines(x,Pstats_K[1,],type='l',lty='dotted')
lines(x,Pstats_K[2,],type='l',lty='dashed')
lines(x,Pstats_K[3,],type='l',lty='dashed')
lines(x,Pstats_K[4,],type='l',lty='dotted')
text(xlimits[1],ylimits_P[1],labels='C',cex=1.5,adj=c(.5,0))
fracplot(Pstats_frac_K,ylimits_P)
vlineplot(x,ylimits_P)

#spearman, p
par(fig=c((ywd+panwd+gap)/totwd,
          (ywd+2*panwd+gap)/totwd,
          (xht+panht+gap)/totht,
          (xht+2*panht+gap)/totht),
    mai=c(0,0,0,0),mgp=c(3,.15,0),tcl=-.25,new=T)
plot(x,Pstats_d,type='l',col="red",xlim=xlimits,ylim=ylimits_P,
     xaxt='n',yaxt='n')
axis(side=1,labels=F)
axis(side=2,labels=F)
lines(x,Pstats_S[1,],type='l',lty='dotted')
lines(x,Pstats_S[2,],type='l',lty='dashed')
lines(x,Pstats_S[3,],type='l',lty='dashed')
lines(x,Pstats_S[4,],type='l',lty='dotted')
text(xlimits[1],ylimits_P[1],labels='D',cex=1.5,adj=c(.5,0))
fracplot(Pstats_frac_S,ylimits_P)
vlineplot(x,ylimits_P)

#kendall, D2
par(fig=c(ywd/totwd,
          (ywd+panwd)/totwd,
          (xht)/totht,
          (xht+panht)/totht),
    mai=c(0,0,0,0),mgp=c(3,.15,0),tcl=-.25,new=T)
plot(x,D2stats_d,type='l',col="red",xlim=xlimits,ylim=ylimits_D2)
mtext(side=1,line=1,text="Diagonal slice")
mtext(side=2,line=1,text=expression(D^{2}))
axis(side=1,labels=F)
lines(x,D2stats_K[1,],type='l',lty='dotted')
lines(x,D2stats_K[2,],type='l',lty='dashed')
lines(x,D2stats_K[3,],type='l',lty='dashed')
lines(x,D2stats_K[4,],type='l',lty='dotted')
text(xlimits[1],ylimits_D2[1],labels='E',cex=1.5,adj=c(.5,0))
fracplot(D2stats_frac_K,ylimits_D2)
vlineplot(x,ylimits_D2)

#spearman, P
par(fig=c((ywd+panwd+gap)/totwd,
          (ywd+2*panwd+gap)/totwd,
          (xht)/totht,
          (xht+panht)/totht),
    mai=c(0,0,0,0),mgp=c(3,.15,0),tcl=-.25,new=T)
plot(x,D2stats_d,type='l',col="red",xlim=xlimits,ylim=ylimits_D2,
     yaxt='n')
mtext(side=1,line=1,text="Diagonal slice")
axis(side=1,labels=F)
axis(side=2,labels=F)
lines(x,D2stats_S[1,],type='l',lty='dotted')
lines(x,D2stats_S[2,],type='l',lty='dashed')
lines(x,D2stats_S[3,],type='l',lty='dashed')
lines(x,D2stats_S[4,],type='l',lty='dotted')
text(xlimits[1],ylimits_D2[1],labels='F',cex=1.5,adj=c(.5,0))
fracplot(D2stats_frac_S,ylimits_D2)
vlineplot(x,ylimits_D2)

@@

![Nonparametric tests for tail dependence and other deviations from a normal copula for soil C and N data. As described in Methods, each statistic was computed on the data using the ranges $0-0.1$, $0.1-0.2$, ..., $0.9-1$ (red lines), and was also computed using the same ranges for 1000 normal-copula surrogate datasets (dashed lines show 0.025 and 0.975 quantiles of these results and dotted lines show 0.005 and 0.995 quantiles).  When red lines were outside dashed lines, text at the top of plots indicates how many surrogate values the data value was less than or greater than. When $\cor$ values (respectively, $\Ps$ or $\Dsq$ values) were greater than surrogates, it means dependence in that part of the distributions was stronger than (respectively, stronger than or weaker than for $\Ps$ or $\Dsq$) expected from a normal-copula null hypothesis. \label{fig_soilCN_nonparam}](./Results/stat_results/stat_soilCN/CNdata_NonparamTailDep.pdf)

@@

<!--Now make and display a table, this one about asymmetry of tail dependence-->
```{r plot_soilCN_asymmtry_taildep, echo=F}
atdres<-data.frame(Statistic=c("$\\cor_{0,0.1}-\\cor_{0.9,1}$","$\\Ps_{0,0.1}-\\Ps_{0.9,1}$","$\\Dsq_{0.9,1}-\\Dsq_{0,0.1}$"),
                   Kendall=rep("",3),
                   Spearman=rep("",3),stringsAsFactors = F)
fractxt<-function(fracval)
{
  ptxt<-''
  if (fracval>.5*numsurrog)
  {
    ptxt<-paste(">",fracval,sep='')
  } 
  if (fracval<=.5*numsurrog)
  {
    ptxt<-paste("<",numsurrog-fracval,sep='')
  }
  return(ptxt)
}
atdres[1,2]<-fractxt(corlmcoru_frac_K)
atdres[1,3]<-fractxt(corlmcoru_frac_S)
atdres[2,2]<-fractxt(PlmPu_frac_K)
atdres[2,3]<-fractxt(PlmPu_frac_S)
atdres[3,2]<-fractxt(D2umD2l_frac_K)
atdres[3,3]<-fractxt(D2umD2l_frac_S)
```

```{r tab_soilCN_asym, echo=F, results="markup"}
knitr::kable(atdres,
             format="pandoc",
             caption = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis. Three statistics are listed in the left column that measured asymmetry of tail dependence by comparing the distribution ranges $0-0.1$ and $0.9-1$ (Methods). One thousand Kendall-preserving and 1000 Spearman-preserving surrogates with normal copula structure were created, and the same statistics were computed for the surrogates. A table entry $<N$ indicates the value of the given statistic on the data was less than its value on $N$ of the surrogates, so entries of the form $<X$ for $X$ equal to $975$ or above indicate that upper-tail dependence was significantly stronger than lower-tail dependence. Recall that Spearman-preserving surrogates are more appropriate for the $\\cor$ statistic (Figure \\ref{fig_soilCN_nonparam} caption).\\label{tab_soilCN_asym}",
             booktabs=T)
```

@@

<!--Shya to implement the modelling we discussed on 2018 04 12 and make results appear here!-->
```{r cause4copula, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"))}
source("Cause4copula.R")
set.seed(seed)
#---------------------------------------
pdf("./Results/Cause4copula_results/compare_params_pGOF.pdf", width=12, height=6)
op<-par(mfrow=c(2,4),mar=c(3,3.5,3,3.5), mgp=c(1.5,0.5,0))

@@

op2<-par(fig = c(0, 1, 0, 1), oma = c(0, 0, 0, 0), mar = c(0, 0, 0, 0), new = TRUE)
plot(0, 0, type = "n", bty = "n", xaxt = "n", yaxt = "n")
legend("top", c("noise","population"), col = c("red", "blue"),
       cex = 0.8, pch = c(2, 6), lty = c(1, 1), xpd = TRUE, horiz = TRUE, inset = c(0,0), 
       bty = "n") 
par(op2)
dev.off()
#-------------------------------------------------------------
#pdf("./Results/Cause4copula_results/Clayton_spearman.pdf")
#Plotter_Cause4copula_stat(numsim=500,fcode=3,method="spearman",lb=0,ub=0.1)
#dev.off()

>>>>

## Phylogenetic data  \label{Phylo_data}
```{r calculation_phylo_data, echo=F, results="hide"}
source("phylo_dat_fn.R")
phylo_dat<-read.csv("./Data/Anolis/contrasts.csv",header = T)

@@

### Non-parametric analysis of tail dependence \label{Ex_SoilCN_NPA}

```{r stat_soilCN_graphic_approach, echo=F, results="hide", cache=T, cache.extra=list(seed,v_CN,mtime("bivfunctionplot.R"),mtime("CopulaFunctions_flexible.R"),mtime("copsurrog2d.R"))}
source("bivfunctionplot.R")
set.seed(seed) 
stat_soilCN_ga<-bivfunctionplot(v=v_CN,resloc="./Results/stat_results/stat_soilCN/",nametag="soilCN",numbin=10)
```

@@

![Nonparametric tests for tail dependence and other deviations from a normal copula for soil C and N data. As described in Methods, each statistic was computed on the data using the ranges $0-0.1$, $0.1-0.2$, ..., $0.9-1$ (red lines), and was also computed using the same ranges for 1000 normal-copula surrogate datasets (dashed lines show 0.025 and 0.975 quantiles of these results and dotted lines show 0.005 and 0.995 quantiles).  When red lines were outside dashed lines, text at the top of plots indicates how many surrogate values the data value was less than or greater than. When $\cor$ values (respectively, $\Ps$ or $\Dsq$ values) were greater than surrogates, it means dependence in that part of the distributions was stronger than (respectively, stronger than or weaker than for $\Ps$ or $\Dsq$) expected from a normal-copula null hypothesis. \label{fig_soilCN_nonparam}](./Results/stat_results/stat_soilCN/soilCN_bivfunctionplot.pdf)

@@

<!--Now make and display a table, this one about asymmetry of tail dependence-->
```{r make_table_stat_fn, echo=F}

fractxt<-function(fracval,numsurrog=1000){
  ptxt<-''
  if (fracval>.5*numsurrog){                        # why 0.5 factor?
    ptxt<-paste(">",fracval,sep='')
  } 
  if (fracval<=.5*numsurrog){
    ptxt<-paste("<",numsurrog-fracval,sep='')
  }
  return(ptxt)
}

make_table_stat_fn<-function(data){

 atdres<-data.frame(Statistic=c("$\\cor_{0,0.1}-\\cor_{0.9,1}$","$\\Ps_{0,0.1}-\\Ps_{0.9,1}$","$\\Dsq_{0.9,1}-\\Dsq_{0,0.1}$"),
                   Kendall=rep("",3),
                   Spearman=rep("",3),stringsAsFactors = F)

 atdres[1,2]<-fractxt(data$corlmcoru_frac_K)
 atdres[1,3]<-fractxt(data$corlmcoru_frac_S)
 atdres[2,2]<-fractxt(data$PlmPu_frac_K)
 atdres[2,3]<-fractxt(data$PlmPu_frac_S)
 atdres[3,2]<-fractxt(data$D2umD2l_frac_K)
 atdres[3,3]<-fractxt(data$D2umD2l_frac_S)

 return(atdres)

}
```

```{r tab_soilCN_asym, echo=F, results="markup"}
tab_soilCN_asym<-make_table_stat_fn(data=stat_soilCN_ga)
knitr::kable(tab_soilCN_asym,
             format="pandoc",
             caption = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis. Three statistics are listed in the left column that measured asymmetry of tail dependence by comparing the distribution ranges $0-0.1$ and $0.9-1$ (Methods). One thousand Kendall-preserving and 1000 Spearman-preserving surrogates with normal copula structure were created, and the same statistics were computed for the surrogates. A table entry $<N$ indicates the value of the given statistic on the data was less than its value on $N$ of the surrogates, so entries of the form $<X$ for $X$ equal to $975$ or above indicate that upper-tail dependence was significantly stronger than lower-tail dependence. Recall that Spearman-preserving surrogates are more appropriate for the $\\cor$ statistic (Figure \\ref{fig_soilCN_nonparam} caption).\\label{tab_soilCN_asym}",
             booktabs=T)
```

## Results: BMR data \label{Ex_BMR}

```{r read_plot_BMR_data, echo=FALSE}
set.seed(seed=101)
source("phylo_dat_fn.R")
#---------------------------------------------------------
BMR_dat<-read.csv("./Data/BMR/bmr-contrasts.csv",header = T)
#class(BMR_dat)
v_BMR<-phylo_dat_fn(data=BMR_dat,i=4,j=3,ploton = F)

pdf("./Results/BMR_results/BMR_vs_lnmass.pdf")
plot(v_BMR[,1],v_BMR[,2],col="blue",xlab="ln(mass)",ylab="BMR") # copula plot btw ln(Mass) vs. BMR
dev.off()
```

### Model selection approach \label{Ex_BMR_Model_selection}

```{r bivMS_BMR, echo=F, cache=T, cache.extra=list(seed,v_BMR,mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
set.seed(seed)
source("OurBiCopSelect.R")
#families<-c(1,3:10,13:14,16:20) 
BivMS_BMR<-OurBiCopSelect(u1=v_BMR[,1],u2=v_BMR[,2],families=c(1,3:10,13:14,16:20),
                          level=0.05,AICBIC="AIC",numBSsmall=100,pthresh=0.2,numBSlarge=1000,gofnormal=F,status=F)
saveRDS(BivMS_BMR,file="./Results/BMR_results/BivMS_BMR_lnmass.RDS")
```

### Non-parametric analysis of tail dependence \label{Ex_BMR_NPA}

```{r stat_BMR_graphic_approach, echo=F, results="hide", cache=T, cache.extra=list(seed,v_BMR,mtime("bivfunctionplot.R"),mtime("CopulaFunctions_flexible.R"),mtime("copsurrog2d.R"))}
source("bivfunctionplot.R")
set.seed(seed) 
# Now do NPA for v_BMR
# If "F"/"SBB8" is the best fit : then it should be symmetric tail dep (0) : Then still I need to do NPA ?
# May be : because it will also tell me how they are different from "N" copula in different sections?
source("bivfunctionplot.R")
stat_BMR_ga<-bivfunctionplot(v=v_BMR,resloc="./Results/BMR_results/",nametag="BMR",numbin = 10)
```

```{r }
tab_BMR_asym<-make_table_stat_fn(data=stat_BMR_ga)
knitr::kable(tab_BMR_asym)
```

@@

<!--Shya to implement the modelling we discussed on 2018 04 12 and make results appear here!-->
```{r cause4copula, echo=F, cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"))}
source("Cause4copula.R")
set.seed(seed=101)
#---------------------------------------
pdf("./Results/Cause4copula_results/compare_params_pGOF.pdf", width=12, height=6)
op<-par(mfrow=c(2,4),mar=c(3,3.5,3,3.5), mgp=c(1.5,0.5,0))

@@

op2<-par(fig = c(0, 1, 0, 1), oma = c(0, 0, 0, 0), mar = c(0, 0, 0, 0), new = TRUE)
plot(0, 0, type = "n", bty = "n", xaxt = "n", yaxt = "n")
legend("top", c("noise","population", "p_CvM", "p_KS"), col = c("red", "blue", "magenta", "green2"),
       cex = 0.8, pch = c(2, 6, 16, 16), lty = c(1, 1, NA, NA), xpd = TRUE, horiz = TRUE, inset = c(0,0), 
       bty = "n") 
par(op2)
dev.off()

#-------------------------------------------------------------
#pdf("./Results/Cause4copula_results/Clayton_spearman.pdf")
#Plotter_Cause4copula_stat(numsim=500,fcode=3,method="spearman",lb=0,ub=0.1)
#dev.off()
